### 2018-07-16 paper/sphinxes.tex
Sphinxes: clarifies the random selection of the next node
Removes ref to LIONESS (fixes #48)
Adds \prp' and \hash_{\prp'} to list of primitives

  \item \(\prp\colon \bin^\kappa\times \bin^{l_\prp} \to \bin^{l_\prp}\) is 
    \iac{PRP}.
    It can be instantiated using the LIONESS block cipher~\cite{LIONESS}.

  \item \(\hash_\mac, \hash_\prg, \hash_\prp\) are all distinct hash functions 
    of the form \(\bin^\kappa\to \bin^\kappa\).
    They are used as key-derivation functions.

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Send \((\alpha', C', \beta', \gamma')\) to \(L'\).

>>>>

  \item \(\prp\colon \bin^\kappa\times \bin^{l_\prp} \to \bin^{l_\prp}\) is 
    \iac{PRP} used to encrypt the payload data.
    \(l_\prp\) is the maximum length of the payload.
    (Shorter payloads are assumed to be properly padded.)

  \item \(\prp'\colon \bin^\kappa\times \bin^\kappa\times \bin^\kappa\) is 
    another \ac{PRP}.
    It is used to encapsulate keys.

  \item \(\hash_\mac, \hash_\prg, \hash_\prp. \hash_{\prp'}\) are all distinct 
    hash functions of the form \(\bin^\kappa\to \bin^\kappa\).
    They are used as key-derivation functions.

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Choose a node \(n\rgets L'\) uniformly at random.
Send \((\alpha', C', \beta', \gamma')\) to \(n\).
If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
If all nodes in \(L'\) fails, the algorithm fails.
